Global search algorithm with local tuning for solving mixed-integer global optimization problems \thanks{This study was supported by the .}

### 2021-04-10 2021/MOTOR_BarkalovLebedev/MOTOR2021.tex
fix some mistakes in the reference list

\bibitem{c1} Miettinen, K.: Nonlinear Multiobjective Optimization. Springer (1999).
\bibitem{c2} Ehrgott, M.: Multicriteria Optimization. Springer (2nd ed., 2010).
\bibitem{c3} Collette, Y., Siarry, P.:  Multiobjective Optimization: Principles and Case Studies (Decision Engineering). Springer (2011).
\bibitem{c4} Marler, R.T., Arora, J.S.: Multi-Objective Optimization: Concepts and Methods for Engineering. VDM Verlag (2009).
\bibitem{c5} Pardalos, P.M., {\v Z}ilinskas, A., {\v Z}ilinskas, J.: Non-Convex Multi-Objective Optimization. Springer (2017).
\bibitem{c6} Marler, R.T., Arora, J.S.: Survey of multi-objective optimization methods for engineering. Struct. Multidisciplinary Optimization \textbf{26}, 369--395 (2004).
\bibitem{c7}  Figueira, J., Greco, S., Ehrgott, M., eds.: Multiple criteria decision analysis: state of the art surveys. New York (NY). Springer (2005).
\bibitem{c8} Zavadskas, E.K., Turskis, Z., Kildien{\. e}, S.: State of art surveys of overviews on MCDM/MADM methods. Technological and Economic Development of Economy, \textbf{20}, 165--179 (2014).
\bibitem{c9} Hillermeier, C., Jahn, J.: Multiobjective optimization: survey of methods and industrial applications. Surv. Math. Ind. \textbf{11}, 1--42 (2005).
\bibitem{c10} Collette, Y., Siarry, P.: Multiobjective Optimization: Principles and Case Studies. Decision Engineering. Springer, Heidelberg (2011). \doi{10.1007/978-3-662-08883-8}
\bibitem{c11} Eichfelder, G.: Scalarizations for adaptively solving multi-objective optimization problems. Comput. Optim. Appl. \textbf{44}, 249--273 (2009).
\bibitem{c12} Figueira, J., Liefooghe, A., Talbi, E., Wierzbicki, A.: A parallel multiple reference point approach for multi-objective optimization. European Journal of Operational Research \textbf{205}(2), 390--400 (2010). \doi{10.1016/j.ejor.2009.12.027}
\bibitem{c35} Gergel, V.: An unified approach to use of coprocessors of various types for solving global optimization problems. 2nd International Conference on Mathematics and Computers in Sciences and in Industry, 13--18 (2015). \doi{10.1109/MCSI.2015.18}
\bibitem{c36} Gergel, V.P., Kozinov, E.A.: Accelerating multicriterial optimization by the intensive exploitation of accumulated search data. AIP Conference Proceedings \textbf{1776}, 090003 (2016). \doi{10.1063/1.4965367}
\bibitem{c37} Gergel, V., Kozinov, E.: Efficient multicriterial optimization based on intensive reuse of search information. Journal of Global Optimization \textbf{71}(1), 73--90 (2018).
\bibitem{c44} Gergel, V., Kozinov, E., Barkalov, K.: Computationally efficient approach for solving lexicographic multicriteria optimization problems. Optim. Lett. (2020). \doi{10.1007/s11590-020-01668-y}
\bibitem{c13} Zhigljavsky, A.A.: Theory of Global Random Search. Dordrecht: Kluwer Academic Publishers (1991).
\bibitem{c14} Pint{\' e}r, J.D.: Global optimization in Action (continuous and Lipschitz optimization: algorithms, implementations and applications). Kluwer Academic Publishers, Dortrecht (1996).
\bibitem{c15} Strongin, R., Sergeyev, Ya.: Global optimization with non-convex constraints. Sequential and parallel algorithms. Kluwer Academic Publishers, Dordrecht (2nd ed. 2013, 3rd ed. 2014).
\bibitem{c16} Yang, X.-S.: Nature-inspired metaheuristic algorithms. Luniver Press, Frome (2008).
\bibitem{c17} Locatelli, M., Schoen, F.: Global Optimization: Theory, Algorithms, and Applications. SIAM (2013).

@@

\bibitem{c19} Floudas, C.A., Pardalos, M.P.: Recent Advances in Global Optimization. Princeton University Press (2016).
\bibitem{c20} Sergeyev, Y.D., Kvasov, D.E.: Deterministic Global Optimization: An Introduction to the Diagonal Approach. Springer, New York (2017). 
\bibitem{c21} Sergeyev, Y.D., Strongin, R.G., Lera, D.: Introduction to global optimization exploiting space-filling curves. Springer (2013).
\bibitem{c22} Piyavskij, S.: An algorithm for finding the absolute extremum of a function. Computational Mathematics and Mathematical Physics \textbf{12}, 57--67 (1972).
\bibitem{c23} Shubert, B.O.: A sequential method seeking the global maximum of a function. SIAM Journal on Numerical Analysis \textbf{9}, 379--388 (1972).
\bibitem{c24} Strongin, R.G.: Multiextremal minimization. Autom. Remote Control \textbf{7}, 1085--1088 (1970).
\bibitem{c25} Galperin, E.A.: The cubic algorithm. Journal of Mathematical Analysis and Applications \textbf{112}, 635--640 (1985).
\bibitem{c26} Breiman, L., Cutler, A.: A deterministic algorithm for global optimization, Mathematical Programming \textbf{58}, 179--199 (1993).
\bibitem{c27} Baritompa, W.: Accelerations for a variety of global optimization methods. Journal of Global Optimization \textbf{4}, 37--45 (1994).
\bibitem{c28} Gergel, V.P.: A method of using derivatives in the minimization of multiextremum functions. Computational Mathematics and Mathematical Physics \textbf{36}(6), 729--742 (1996).
\bibitem{c29} Sergeyev, Y.D.: Global one-dimensional optimization using smooth auxiliary functions. Mathematical Programming \textbf{81}, 127--146 (1998).
\bibitem{c30} Sergeyev, Ya.D., Grishagin, V.A.: Sequential and parallel global optimization algorithms. Optimization Methods and Software \textbf{3}, 111--124 (1994).
\bibitem{c31} Sergeyev, Y.D.: An information global optimization algorithm with local tuning. SIAM J. Optim. \textbf{5}(4), 858--870 (1995).
\bibitem{c32} Sergeyev, Y.D., Grishagin, V.A.: Parallel asynchronous global search and the nested optimization scheme. J. Comput. Anal. Appl. \textbf{3}(2), 123--145 (2001).
\bibitem{c33} Lera, D., Sergeyev, Ya.D.: Deterministic global optimization using space-filling curves and multiple estimates of Lipschitz and Holder constants. Communications in Nonlinear Science and Numerical Simulation \textbf{23}, 328--342 (2015).
\bibitem{c34} Grishagin, V., Israfilov, R., Sergeyev, Y.: Comparative efficiency of dimensionality reduction schemes in global optimization. AIP Conference Proceedings \textbf{1776}, 060011 (2016).
\bibitem{c38} Gergel, V., Barkalov, K., Sysoyev, A.: Globalizer: a novel supercomputer software system for solving time-consuming global optimization problem. Numerical algebra, control and optimization \textbf{8}(1), 47--62 (2018).
\bibitem{c39} {\v Z}ilinskas, A., Zilinskas, J.: Adaptation of a one-step worst-case optimal univariate algorithm of bi-objective Lipschitz optimization to multidimensional problems. Communications in Nonlinear Science and Numerical Simulation \textbf{21}(1-3), 89--98 (2015). \doi{10.1016/j.cnsns.2014.08.025}
\bibitem{c40} Evtushenko, Y., Posypkin, M.: A deterministic algorithm for global multiobjective optimization. Optimization Methods \& Software \textbf{29}(5), 1005--1019 (2014). \doi{10.1080/10556788.2013.854357}
\bibitem{c41} Evtushenko, Y., Posypkin, M.: Method of non-uniform coverages to solve the multicriteria optimization problems with guaranteed accuracy. Autom. Remote Control \textbf{75}(6), 1025--1040 (2014).
\bibitem{c42} Bleuler, S., Laumanns, M., Thiele, L., Zitzler, E.: PISA -- a platform and programming language independent interface for search algorithms. Evolutionary Multi-Criterion Optimization. LNCS \textbf{2632}, 494--508 (2003). \doi{10.1007/3-540-36970-8\_35}
\bibitem{c43} Gaviano, M., Kvasov, D.E, Lera, D., Sergeyev, Ya.D.: Software for generation of classes of test functions with known local and global minima for global optimization. ACM Transactions on Mathematical Software \textbf{29}(4), 469--480 (2003).

>>>>

\bibitem{c1} Miettinen, K.: Nonlinear Multiobjective Optimization. Springer, Boston (1999)
\bibitem{c2} Ehrgott, M.: Multicriteria Optimization, Springer, Berlin (2nd ed., 2010)
\bibitem{c3} Collette, Y., Siarry, P.:  Multiobjective Optimization: Principles and Case Studies (Decision Engineering), Springer, Berlin  (2004)
\bibitem{c4} Marler, R.T., Arora, J.S.: Multi-Objective Optimization: Concepts and Methods for Engineering, VDM Verlag (2009)
\bibitem{c5} Pardalos, P.M., {\v Z}ilinskas, A., {\v Z}ilinskas, J.: Non-Convex Multi-Objective Optimization, Springer (2017)
\bibitem{c6} Marler, R.T., Arora, J.S.: Survey of multi-objective optimization methods for engineering. Struct. Multidiscip. Optim. \textbf{26}, 369--395 (2004)
\bibitem{c7}  Figueira, J., Greco, S., Ehrgott, M., eds.: Multiple Criteria Decision Analysis: State of the Art Surveys. Springer, New York (2005)
\bibitem{c8} Zavadskas, E.K., Turskis, Z., Kildien{\. e}, S.: State of art surveys of overviews on MCDM/MADM methods. Technological and Economic Development of Economy, \textbf{20}, 165--179 (2014)
\bibitem{c9} Hillermeier, C., Jahn, J.: Multiobjective optimization: survey of methods and industrial applications. Surv. Math. Ind. \textbf{11}, 1--42 (2005)
\bibitem{c10} Collette, Y., Siarry, P.: Multiobjective Optimization: Principles and Case Studies. Decision Engineering. Springer, Heidelberg (2011) \doi{10.1007/978-3-662-08883-8}
\bibitem{c11} Eichfelder, G.: Scalarizations for adaptively solving multi-objective optimization problems. Comput. Optim. Appl. \textbf{44}, 249--273 (2009)
\bibitem{c12} Figueira, J., Liefooghe, A., Talbi, E., Wierzbicki, A.: A parallel multiple reference point approach for multi-objective optimization. European Journal of Operational Research \textbf{205}(2), 390--400 (2010) \doi{10.1016/j.ejor.2009.12.027}
\bibitem{c35} Gergel, V.: An unified approach to use of coprocessors of various types for solving global optimization problems. 2nd International Conference on Mathematics and Computers in Sciences and in Industry, 13--18 (2015) \doi{10.1109/MCSI.2015.18}
\bibitem{c36} Gergel, V.P., Kozinov, E.A.: Accelerating multicriterial optimization by the intensive exploitation of accumulated search data. AIP Conference Proceedings \textbf{1776}, 090003 (2016) \doi{10.1063/1.4965367}
\bibitem{c37} Gergel, V., Kozinov, E.: Efficient multicriterial optimization based on intensive reuse of search information. J. Glob. Optim. \textbf{71}(1), 73--90 (2018)
\bibitem{c44} Gergel, V., Kozinov, E., Barkalov, K.: Computationally efficient approach for solving lexicographic multicriteria optimization problems. Optim. Lett. (2020) \doi{10.1007/s11590-020-01668-y}
\bibitem{c13} Zhigljavsky, A.A.: Theory of Global Random Search.  Kluwer Academic Publishers, Dordrecht (1991).
\bibitem{c14} Pint{\' e}r, J.D.: Global Optimization in Action (Continuous and Lipschitz Optimization: Algorithms, Implementations and Applications). Kluwer Academic Publishers, Dortrecht (1996)
\bibitem{c15} Strongin, R., Sergeyev, Ya.: Global Optimization with Non-Convex Constraints. Sequential and Parallel Algorithms. Kluwer Academic Publishers, Dordrecht (2nd ed. 2013, 3rd ed. 2014)
\bibitem{c16} Yang, X.-S.: Nature-inspired Metaheuristic Algorithms. Luniver Press, Frome (2008)
\bibitem{c17} Locatelli, M., Schoen, F.: Global Optimization: Theory, Algorithms, and Applications. SIAM (2013)

@@

\bibitem{c19} Floudas, C.A., Pardalos, M.P.: Recent Advances in Global Optimization. Princeton University Press (2016)
\bibitem{c20} Sergeyev, Y.D., Kvasov, D.E.: Deterministic Global Optimization: An Introduction to the Diagonal Approach. Springer, New York (2017) 
\bibitem{c21} Sergeyev, Y.D., Strongin, R.G., Lera, D.: Introduction to Global Optimization Exploiting Space-Filling Curves. Springer (2013)
\bibitem{c22} Piyavskij, S.: An algorithm for finding the absolute extremum of a function. Comput. Math. Math. Phys. \textbf{12}, 57--67 (1972)
\bibitem{c23} Shubert, B.O.: A sequential method seeking the global maximum of a function. SIAM J. Numer. Anal. \textbf{9}, 379--388 (1972)
\bibitem{c24} Strongin, R.G.: Multiextremal minimization. Autom. Remote Control \textbf{7}, 1085--1088 (1970)
\bibitem{c25} Galperin, E.A.: The cubic algorithm. J. Math. Anal. Appl. \textbf{112}, 635--640 (1985)
\bibitem{c26} Breiman, L., Cutler, A.: A deterministic algorithm for global optimization. Math. Program. \textbf{58}, 179--199 (1993)
\bibitem{c27} Baritompa, W.: Accelerations for a variety of global optimization methods. J. Glob. Optim. \textbf{4}, 37--45 (1994)
\bibitem{c28} Gergel, V.P.: A method of using derivatives in the minimization of multiextremum functions. Comput. Math. Math. Phys. \textbf{36}(6), 729--742 (1996)
\bibitem{c29} Sergeyev, Y.D.: Global one-dimensional optimization using smooth auxiliary functions. Math. Program. \textbf{81}, 127--146 (1998)
\bibitem{c30} Sergeyev, Ya.D., Grishagin, V.A.: Sequential and parallel global optimization algorithms. Optim. Methods Softw.\textbf{3}, 111--124 (1994)
\bibitem{c31} Sergeyev, Y.D.: An information global optimization algorithm with local tuning. SIAM J. Optim. \textbf{5}(4), 858--870 (1995)
\bibitem{c32} Sergeyev, Y.D., Grishagin, V.A.: Parallel asynchronous global search and the nested optimization scheme. J. Comput. Anal. Appl. \textbf{3}(2), 123--145 (2001)
\bibitem{c33} Lera, D., Sergeyev, Ya.D.: Deterministic global optimization using space-filling curves and multiple estimates of Lipschitz and Holder constants. Communications in Nonlinear Science and Numerical Simulation \textbf{23}, 328--342 (2015)
\bibitem{c34} Grishagin, V., Israfilov, R., Sergeyev, Y.: Comparative efficiency of dimensionality reduction schemes in global optimization. AIP Conference Proceedings \textbf{1776}, 060011 (2016)
\bibitem{c38} Gergel, V., Barkalov, K., Sysoyev, A.: Globalizer: a novel supercomputer software system for solving time-consuming global optimization problem. Numerical Algebra, Control and Optimization \textbf{8}(1), 47--62 (2018)
\bibitem{c39} {\v Z}ilinskas, A., Zilinskas, J.: Adaptation of a one-step worst-case optimal univariate algorithm of bi-objective Lipschitz optimization to multidimensional problems. Communications in Nonlinear Science and Numerical Simulation \textbf{21}(1-3), 89--98 (2015) \doi{10.1016/j.cnsns.2014.08.025}
\bibitem{c40} Evtushenko, Y., Posypkin, M.: A deterministic algorithm for global multiobjective optimization. Optim. Methods Softw. \textbf{29}(5), 1005--1019 (2014) \doi{10.1080/10556788.2013.854357}
\bibitem{c41} Evtushenko, Y., Posypkin, M.: Method of non-uniform coverages to solve the multicriteria optimization problems with guaranteed accuracy. Autom. Remote Control \textbf{75}(6), 1025--1040 (2014)
\bibitem{c42} Bleuler, S., Laumanns, M., Thiele, L., Zitzler, E.: PISA -- a platform and programming language independent interface for search algorithms. Lecture Notes in Computer Science \textbf{2632}, 494--508 (2003) \doi{10.1007/3-540-36970-8\_35}
\bibitem{c43} Gaviano, M., Kvasov, D.E, Lera, D., Sergeyev, Ya.D.: Software for generation of classes of test functions with known local and global minima for global optimization. ACM Transactions on Mathematical Software \textbf{29}(4), 469--480 (2003)
